---
title: "Assignment 2"
---

# Assignment 2

**STEP 1** \# We need to install the 'dslabs' library and save the polls_us_election_2016.

```{r}
install.packages("dslabs")
library(dslabs)
data(polls_us_election_2016)
```

**STEP 2** \# Display the first 10 rows.

```{r}
first_ten_rows <- head(polls_us_election_2016,10)
print(first_ten_rows)
```

**STEP 3** \# Calculate and display the total number of NA values in the entire data set. \# I used the sum and is.na functions. is.na function returns a 1 or 0 value, and the sum function sums them.

```{r}
total_na <- sum(is.na(polls_us_election_2016))
print(paste("Total NA values:", total_na))
```

**STEP 4** \# Replace all NA values in the ???polls_us_election_2016??? data set as follows: For numeric columns, replace NA values with your birth year. For character or factor columns, replace NA values with your first name. Store the modified data set as a new object.

```{r}
birth_year <- 2002  
first_name <- "Onur" 

modified_data <- polls_us_election_2016

for (col in names(modified_data)) {
  if (is.numeric(modified_data[[col]])) 
  {
    modified_data[[col]][is.na(modified_data[[col]])] <- birth_year
  } 
  else if (is.factor(modified_data[[col]])) 
  {
    levels(modified_data[[col]]) <- c(levels(modified_data[[col]]), first_name)
    modified_data[[col]][is.na(modified_data[[col]])] <- first_name
  }
  else if (is.character(modified_data[[col]])) 
  {
    modified_data[[col]][is.na(modified_data[[col]])] <- first_name
  }
}
```

**STEP 5** \# Print the first 10 rows of the new data frame and the total number of NAs remaining in the new data frame.

```{r}
print(head(modified_data, 10))

remaining_na <- sum(is.na(modified_data))
cat("Remaining NA values:", remaining_na, "\n")
```
